No Replication Without Process Documentation:  An Assessment of Management

### 2020-04-07 R/MSE manuscript.Rmd
Edit publication and CC filters to match updated database column names; update frequency column selection to match updated database column names

# Filter data by study type
data_pub<-filter(data,IncludeInPublication==TRUE)
data_CC<-filter(data,str_detect(Drivers,"Climate Change"))

@@

#####-- Filter Data by analysis --#####
# Get columns for study summary
summary.col<-c("Citation",
               "Species",
               "Location",
               "System")
# Get columns for study drivers and problem
prob.col<-c("Citation",
            "ProblemDefinition",
            "Drivers",
            "ConsequencePrediction",
            "TradeOffMethod_Exp",
            "TradeOffMethod_Sub",
            "Decision")
# Get columns for frequency analysis
freq.col<-c("ProcessExplicit",
            "ProblemDefinitionExplicit",
            "ObjectivesExplicit",
            "AlternativesExplicit",
            "TradeOffsExplicit",
            "DecisionExplicit",
            "ResultsAdopted")
freq2.col<-c("RolesExplicit",
             "OpenMeetings")
# Get columns for participant analysis
part.col<-c("Leader",
            "Participants",
            "ObjElicitationSource_Exp",
            "ProcedureElicitation_Exp",
            "ObjElicitationSource_Sub",
            "ProcedureElicitation_Sub")
obj.col<-c("ObjType",
           "ObjCategory",
           "ObjDirection",
           "ObjScale")
alt.col<-c("ManagementType",
           "AlternativesEvaluated")
# Get columns for map
map.col<-c("Latitude",
           "Longitude",
           "Citation",
           "Drivers")

@@

freq2.data_pub<-data_pub %>%
    select(all_of(freq2.col)) %>%
    rename("Roles"="RolesExplicit",
           "Open Meetings"="OpenMeetings") %>%
    summarise_all(funs(sum)) %>%
    gather(Explicit) %>%
    mutate(Percent=value/n_pub*100) %>%
    mutate(Explicit=factor(Explicit,levels=
                  c("Roles","Open Meetings"))) %>%
    rename("Number"="value")

>>>>

# Filter data by study type
data_pub<-filter(data,RandomSample==TRUE)
data_CC<-filter(data,str_detect(Drivers,"Climate Change")&UseInPublication==TRUE)

@@

#####-- Filter Data by analysis --#####
# Get columns for study summary
summary.col<-c("Citation",
               "Species",
               "Location",
               "System")
# Get columns for study drivers and problem
prob.col<-c("Citation",
            "ProblemDefinition",
            "Drivers",
            "ConsequencePrediction",
            "TradeOffMethod_Exp",
            "TradeOffMethod_Sub",
            "Decision")
# Get columns for frequency analysis
freq.col<-c("ProcessExplicit",
            "ProblemDefinitionExplicit",
            "ObjectivesExplicit",
            "AlternativesExplicit",
            "TradeOffsExplicit",
            "DecisionExplicit",
            "ResultsAdopted")
freq2.col<-c("RoleSpecification",
             "OpenMeetings")
# Get columns for participant analysis
part.col<-c("Leader",
            "Participants",
            "ObjElicitationSource_Exp",
            "ProcedureElicitation_Exp",
            "ObjElicitationSource_Sub",
            "ProcedureElicitation_Sub")
obj.col<-c("ObjType",
           "ObjCategory",
           "ObjDirection",
           "ObjScale")
alt.col<-c("ManagementType",
           "AlternativesEvaluated")
# Get columns for map
map.col<-c("Latitude",
           "Longitude",
           "Citation",
           "Drivers")

@@

freq2.data_pub<-data_pub %>%
    select(all_of(freq2.col)) %>%
    rename("Roles"="RoleSpecification",
           "Open Meetings"="OpenMeetings") %>%
    summarise_all(funs(sum)) %>%
    gather(Explicit) %>%
    mutate(Percent=value/n_pub*100) %>%
    mutate(Explicit=factor(Explicit,levels=
                  c("Roles","Open Meetings"))) %>%
    rename("Number"="value")
